The LSST DESC 3x2pt Tomography Optimization Challenge

### 2021-02-02 paper/paper.tex
more appendix

\section{Mistakes}
The challenge organizers made a number of mistakes when building and running the challenge.
These do not invalidate our process or results, but we describe them here in the hope of
being useful for future challenge designers.

@@

\subsection{Infrastructure}

\begin{itemize}
    \item 
    \item Infrastructure for checking submissions
    \item Guidance for users regarding caching and batch processing
    \item Timing
    \item Training set size
    \item Advertisement
\end{itemize}

>>>>

\section{Mistakes}
The challenge organizers made a number of mistakes when building and running the challenge.
These do not invalidate our process or results, but we describe some of them here in the hope of
being useful for future challenge designers.

@@

\subsection{Infrastructure}
Since submissions could use a wide variety of libraries and dependencies, it was extremely
difficult after the challenge was complete to build appropriate environments for all the challenges
in order to run the methods on additional data sets. In retrospect, a robust and careful
continuous integration tool with a mechanism for entrants to specify an environment (for example, a 
container or a {\sc conda} requirements file) could have been used to simplify this and ensure
all methods could be easily run by the organizers.

Once additional issue, though, was that many methods required GPUs to train in a reasonable time,
and specifying an environment on these systems can be more complicated.

\subsection{Guidance on caching \& batch processing}
Since the training process for the challenge could be slow for some algorithms, many entries
very reasonably cached trained models or other values for later use.  In some cases these
cached values were then incorrectly picked up by subsequent runs on new data sets, leading
to (at best) crashes and at worst silently poor scores.  We should have provided an explicit
caching mechanism for entrants to avoid such issues.

Additionally, the challenge supplied the data described in Section \ref{sec:data} to entrants,
and some assumed that it was safe to hard-code specific paths to them or
otherwise assume fixed data inputs.  This led to problems when switching to new test data sets. 
Again, a requirement enforced by continuous integration could have checked this.
